\abschnitt{Recent WG21 History}\label{wg21_history}

In St. Louis in June 2024,
\href{https://docs.google.com/document/d/1ebdFai3h2Y4g5NayNf_pG6Gl2qidYdF6G-smMWNw-Go/edit?tab=t.0#heading=h.9aqgmrf0hvh1}{LWG tentatively approved}
P0876 Library wording.

In Tokyo in March 2024, CWG finished initial P0876 Core wording review, with
\href{https://wiki.edg.com/bin/view/Wg21tokyo2024/CoreWorkingGroup#D0876R16_fiber_context}{one requested change}:
that P0876 mandate per-fiber exception state. That required EWG approval.

In St. Louis in June 2024,
\href{https://wiki.edg.com/bin/view/Wg21stlouis2024/NotesEWGP0876}{EWG approved} the change:

\begin{table}[ht]
\begin{tabular}{|r|r|r|r|r|} % right-just columns (5 columns)
\hline %inserts horizontal line
SF & F & N & A & SA \\ [0.5ex] % inserts table heading
\hline % inserts single horizontal line
6 & 8 & 3 & 0 & 0 \\ % [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
\end{table}

However, EWG did not forward P0876 back to CWG, requesting implementation
experience with the proposed change.

In Wrocław in November 2024, Nat Goodspeed presented implementation experience
with libstdc++.
\href{https://wiki.edg.com/bin/view/Wg21wroclaw2024/NotesEWGP0876}{Microsoft requested}
time to consult the backend team. EWG agreed to defer to Hagenberg.

In Hagenberg in February 2025, late in the week,
\href{https://lists.isocpp.org/ext/2025/02/25138.php}{Microsoft conceded} that
per-fiber exception state is implementable with the MSVC runtime (while voicing
performance concerns). Unfortunately this response arrived so late that EWG
ran out of time without considering P0876.

In Sofia in June 2025,
\href{https://docs.google.com/document/d/1wItX212LurEjkJK53XxnxumciqTRzxTSTJ48GwFihpE/edit?tab=t.0#heading=h.zc6lxwkrnobj}{EWG forwarded P0876}
back to CWG and LWG for inclusion in C++26:

\begin{table}[ht]
\begin{tabular}{|r|r|r|r|r|} % right-just columns (5 columns)
\hline %inserts horizontal line
SF & F & N & A & SA \\ [0.5ex] % inserts table heading
\hline % inserts single horizontal line
10 & 14 & 4 & 5 & 1 \\ % [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
\end{table}

But both CWG and LWG ran out of time in Sofia without considering P0876,
thereby postponing it to C++29.

Concerning a <feature> that fails to make the deadline for C++<NN>,
\href{https://www.open-std.org/jtc1/sc22/wg21/docs/papers/2024/p1000r6.pdf}{P1000R6}
says:
``Just wait a couple more meetings and C++<NN+3> will be open for business and <feature> can be
the first thing voted into the C++<NN+3> working draft.''

This is the promise of the train model. It matters to all of us that the train
model works as promised.
